Paper

### 2025-03-12 paper/paper.qmd
post predictive check figures

```{r fig-consts-sims-coloured, include=FALSE}
#| echo: false
#| fig.width: 18
#| fig.height: 8
#| message: false
consts_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  #slice_sample(n=10) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(siminputrow, date_sim) %>%
  summarise(rate = mean(rate)) %>%
  ggplot(aes(x = date_sim,
             y = rate,
             color = factor(`siminputrow`))) +
  geom_line() +
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "black") +
  guides(color="none")
```

@@

@@

>>>>

```{r fig-consts-sims-coloured, include=TRUE}
#| echo: false
#| fig.width: 18
#| fig.height: 8
#| message: false
consts_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  #slice_sample(n=10) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(siminputrow, date_sim) %>%
  summarise(rate = mean(rate)) %>%
  ggplot(aes(x = date_sim,
             y = rate,
             color = factor(`siminputrow`))) +
  geom_line() +
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "black") +
  guides(color="none")
```

@@

```{r fig-single-outbreak-coloured, include=TRUE}
#| echo: false
#| fig.width: 18
#| fig.height: 8
#| message: false
single_outbreak_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  #slice_sample(n=10) %>% 
  dplyr::select(!`siminputrow`) %>% 
  pivot_longer(cols = !c(`random-seed`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(date_sim, `random-seed`) %>%
  summarise(rate = mean(rate)) %>%
  ggplot(aes(x = date_sim,
             y = rate,
             color = factor(`random-seed`))) +
  geom_line() +
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "black") +
  guides(color="none")
```

@@

```{r fig-posterior-predictive-check, include=TRUE}
#| echo: false
posterior_predictive_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(date_sim) %>%
  summarise(m = median(rate),
            q_high = quantile(rate, 0.75),
            q_low = quantile(rate, 0.25),
            .groups = "keep") %>%
  ggplot() +
  geom_line(aes(x = date_sim, y = m)) +
  geom_line(aes(x = date_sim, y = q_high), linetype='dashed') +
  geom_line(aes(x = date_sim, y = q_low), linetype='dashed') + 
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "red") +
  guides(color="none")
```

```{r fig-posterior-predictive-check-coloured, include=TRUE}
#| echo: false
#| message: false
posterior_predictive_sim_rates %>% 
  pivot_wider(names_from = date_sim, values_from = rate) %>% 
  #slice_sample(n=10) %>% 
  pivot_longer(cols = !c(`random-seed`, `siminputrow`), names_to = "date_sim", values_to = "rate") %>% 
  mutate(date_sim = ymd(date_sim)) %>% 
  group_by(siminputrow, date_sim) %>%
  summarise(rate = mean(rate)) %>%
  ggplot(aes(x = date_sim,
             y = rate,
             color = factor(`siminputrow`))) +
  geom_line() +
  geom_line(data = long_observed_ss, aes(x = x, y = rates), color = "black") +
  guides(color="none")
```
